Augraphy: An Augmentation Pipeline API for Modern Document Images

### 2023-02-11 paper.tex
add shabbypages denoised image
fix shabbyreal_denoised ref

\subsection{Results}
Sample predictions from the model on the validation task are presented in Figure \ref{fig:shabbyreal_denoising}. The SSIM score indicates that these models generalize very well, though they do overcompensate for shadowing features around text, by increasing the line thickness in the prediction, resulting in a bold font.

@@

>>>>

\subsection{Results}
Sample predictions from the model on the validation task are presented in Figure \ref{fig:shabbyreal_denoised}. The SSIM score indicates that these models generalize very well, though they do overcompensate for shadowing features around text, by increasing the line thickness in the prediction, resulting in a bold font.

@@

\begin{figure}
\centering
\includegraphics[width=0.98\columnwidth]{figures/shabbypages_denoising.png}
\caption{Sample \emph{ShabbyPages} noisy images (left), denoised by Shabby\_NAFNet (center), and groundtruth (right).}
\label{fig:shabbypages_denoising}
\end{figure}
